### 2017-04-26 paper/frag_implementation.tex

Our protocol is similar to the UDP protocol for communication between the client
and detour. The kernel sends a message of type \texttt{DETOUR_C_REQ} to a
``multicast group'' which the client daemon subscribes to. This message contains
the necessary parameters (remote address, remote port). The client daemon may
reply to the kernel with \texttt{DETOUR_C_ADD} commands, which add detour
entries, and \texttt{DETOUR_C_DEL} commands, which remove them.

@@

Upon creation, our path manager enqueues a task to be executed in a long-running
kernel thread. This task first sends a message to userspace on the Generic
Netlink socket, requesting a detour. Then, the task looks through an internal
list of detours. The kernel maintains two lists of detours. The first is a list
of OpenVPN detours. These detours are not specific to the remote port and host.
The second list contains NAT tunnels which were created by the client daemon and
sent to the kernel via the \texttt{DETOUR_C_ADD} command.

@@

When the client receives a \texttt{DETOUR_C_ADD} command, it first adds the
details of the tunnel to its internal list. Then, if the tunnel was a NAT
tunnel, it wakes all the path managers so that they can attempt to create a
subflow through that tunnel.

>>>>

Our protocol is similar to the UDP protocol for communication between the client
and detour. The kernel sends a message of type \texttt{DETOUR\_C\_REQ} to a
``multicast group'' which the client daemon subscribes to. This message contains
the necessary parameters (remote address, remote port). The client daemon may
reply to the kernel with \texttt{DETOUR\_C\_ADD} commands, which add detour
entries, and \texttt{DETOUR\_C\_DEL} commands, which remove them.

@@

Upon creation, our path manager enqueues a task to be executed in a long-running
kernel thread. This task first sends a message to userspace on the Generic
Netlink socket, requesting a detour. Then, the task looks through an internal
list of detours. The kernel maintains two lists of detours. The first is a list
of OpenVPN detours. These detours are not specific to the remote port and host.
The second list contains NAT tunnels which were created by the client daemon and
sent to the kernel via the \texttt{DETOUR\_C\_ADD} command.

@@

When the client receives a \texttt{DETOUR\_C\_ADD} command, it first adds the
details of the tunnel to its internal list. Then, if the tunnel was a NAT
tunnel, it wakes all the path managers so that they can attempt to create a
subflow through that tunnel.
